Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-18 paper.tex
Further compress rule state figure

\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \begin{subcaptiongroup}
      \subcaptionlistentry{}
      \begin{minipage}{0.5\textwidth}
        \begin{tikzpicture}[outer sep=auto, level distance=12mm, scale=0.50]
          \node at (-2,0) {\captiontext*{}\label{fig:example1:state1}};
          \node[xshift = 0] {$H_{y}$}
            child {node {2}
              child {node {$301$}
                child {node {$\{h₁\}$}}}
            %  child {node {$300$}
            %    child {node {$\{\}$}}}
            };
          \node[xshift=80] {$M_y$}
            child {node {1}
              child {node {$302$}
                child {node {$\{[h₁]\}$}}}
            %  child {node {$301$}
            %    child {node {$\{\}$}}}
            };
            %child {node[xshift=20] {2}
            %  child {node {$301$}
            %    child {node[yshift=-2em] {$\{\}$}}}};
        \end{tikzpicture}
      \end{minipage}
    \end{subcaptiongroup}
    \begin{subcaptiongroup}
      \subcaptionlistentry{}
      \begin{minipage}{0.5\textwidth}
        \begin{tikzpicture}[outer sep=auto, level distance=12mm, scale=0.50]
          \node at (-2,0) {\captiontext*{}\label{fig:example1:state2}};
          \node[xshift = 0] {$H_y$}
            child {node {2}
              child {node {$301$}
                child {node {$\{h₁\}$}}}
              child {node {$300$}
                child {node {$\{h₂\}$}}}
            };
          \node[xshift=80] {$M_y$}
            child {node {1}
              child[xshift=-20] {node {$302$}
                child {node {$\{[h₁]\}$}}}
              child[xshift=20] {node {$301$}
                child {node {$\{[h₂]\}$}}}
            };
        \end{tikzpicture}
      \end{minipage}
    \end{subcaptiongroup}
  \end{minipage}
  \\[1em]
  \begin{subcaptiongroup}
    \subcaptionlistentry{}
    \begin{minipage}{\textwidth}
      \begin{tikzpicture}[outer sep=auto, level distance=12mm, scale=0.50]
        \node at (-2,0) {\captiontext*{}\label{fig:example2:state1}};
        \node[xshift = 0] {$H_x$}
            child {node {2}
                child {node {$a$}
                    child {node {$\{h_1\}$}}}
                %child {node {$b$}
                %    child {node {$\{ \}$}}}
                };
        \node[xshift = 80] {$H_y$}
            child {node {2}
                child {node {$a$}
                    child {node {$\{h_1\}$}}}
                %child {node {$b$}
                %    child {node {$\{ \}$}}}
                    };
        \node[xshift = 160, yshift = 0] {$M_x$}
            child {node {1}
                child {node {$a$}
                    child {node {$\{[h_2]\}$}}}
                %child {node {$b$}
                %   child {node {$\{ \}$}}}
                    };
            %child[xshift = 20] {node {2}
            %    child {node {$a$}
            %        child {node {$\{\}$}}}
            %    child {node {$b$}
            %        child {node {$\{ \}$}}}
            %};
        \node[xshift = 240, yshift = 0] {$M_y$}
            child {node {1}
            %    child {node {$a$}
            %        child {node {$\{ \}$}}}
                child {node {$b$}
                    child {node {$\{[h_2]\}$}}}
            };
            %child[xshift = 20] {node {2}
            %    child {node {$a$}
            %        child {node {$\{\}$}}}
            %    child {node {$b$}
            %        child {node {$\{ \}$}}}
            %};
      \end{tikzpicture}
    \end{minipage}
  \end{subcaptiongroup}
  \\[1em]
  \begin{subcaptiongroup}
    \subcaptionlistentry{}
    \begin{minipage}{\textwidth}
      \begin{tikzpicture}[outer sep=auto, level distance=12mm, scale=0.50]
        \node at (-2,0) {\captiontext*{}\label{fig:example2:state2}};
        \node[xshift = 0] {$H_x$}
          child {node {2}
              child {node {$a$}
                  child {node {$\{h_1, h_3\}$}}}
              %child {node {$b$}
              %    child {node {$\{ \}$}}}
              };
        \node[xshift = 80] {$H_y$}
          child {node {2}
              child {node {$a$}
                  child {node {$\{h_1\}$}}}
              child {node {$b$}
                  child {node {$\{h_3\}$}}}};
        \node[xshift = 160, yshift = 0] {$M_x$}
          child {node {1}
              child {node {$a$}
                  child {node {$\{[h_2]\}$}}}
              %child {node {$b$}
              %   child {node {$\{ \}$}}}
                  };
        \node[xshift = 240, yshift = 0] {$M_y$}
          child {node {1}
          %    child {node {$a$}
          %        child {node {$\{ \}$}}}
              child {node {$b$}
                  child {node {$\{[h_2]\}$}}}
          };
      \end{tikzpicture}
    \end{minipage}
  \end{subcaptiongroup}
  \caption{Rule states encountered during Examples~1 and~2}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \begin{subcaptiongroup}
      \subcaptionlistentry{}
      \begin{minipage}{0.5\textwidth}
        \begin{tikzpicture}[outer sep=auto, level distance=4em, scale=0.50]
          \node at (-2,0) {\captiontext*{}\label{fig:example1:state1}};
          \node {$H_{y}\colon$};
          \node at (1.5,0) {2}
            child {node {$301$}
              child {node {$\{h₁\}$}}};
          \node at (5, 0) {$M_y\colon$};
          \node at (6.5, 0) {1}
            child {node {$302$}
              child {node {$\{[h₁]\}$}}};
        \end{tikzpicture}
      \end{minipage}
    \end{subcaptiongroup}
    \begin{subcaptiongroup}
      \subcaptionlistentry{}
      \begin{minipage}{0.5\textwidth}
        \begin{tikzpicture}[outer sep=auto, level distance=4em, scale=0.50]
          \node at (-2,0) {\captiontext*{}\label{fig:example1:state2}};
          \node {$H_y\colon$};
          \node at (1.5, 0) {2}
            child {node[xshift=-2] {$301$}
              child {node {$\{h₁\}$}}}
            child {node[xshift=2] {$300$}
              child {node {$\{h₂\}$}}};
          \node at (5, 0) {$M_y\colon$};
          \node at (6.5, 0) {1}
            child {node[xshift=-2] {$302$}
              child {node {$\{[h₁]\}$}}}
            child {node[xshift=2] {$301$}
              child {node {$\{[h₂]\}$}}};
        \end{tikzpicture}
      \end{minipage}
    \end{subcaptiongroup}
  \end{minipage}
  \\[1em]
  \begin{subcaptiongroup}
    \subcaptionlistentry{}
    \begin{minipage}{\textwidth}
      \begin{tikzpicture}[outer sep=auto, level distance=4em, scale=0.50]
        \node at (-2,0) {\captiontext*{}\label{fig:example2:state1}};
        \node {$H_x\colon$};
        \node at (1.5, 0) {2}
          child {node {$a$}
            child {node {$\{h_1\}$}}};
        \node at (5, 0) {$H_y\colon$};
        \node at (6.5, 0) {2}
          child {node {$a$}
            child {node {$\{h_1\}$}}};
        \node at (10, 0) {$M_x\colon$};
        \node at (11.5, 0) {1}
          child {node {$a$}
            child {node {$\{[h_2]\}$}}};
        \node at (15, 0) {$M_y\colon$};
        \node at (16.5, 0) {1}
          child {node {$b$}
            child {node {$\{[h_2]\}$}}};
      \end{tikzpicture}
    \end{minipage}
  \end{subcaptiongroup}
  \\[1em]
  \begin{subcaptiongroup}
    \subcaptionlistentry{}
    \begin{minipage}{\textwidth}
      \begin{tikzpicture}[outer sep=auto, level distance=12mm, scale=0.50]
        \node at (-2,0) {\captiontext*{}\label{fig:example2:state2}};
        \node {$H_{x}\colon$};
        \node at (1.5, 0) {2}
          child {node {$a$}
            child {node {$\{h_1, h_3\}$}}};
        \node at (5, 0) {$H_y\colon$};
        \node at (6.5, 0) {2}
          child {node {$a$}
            child {node {$\{h_1\}$}}}
          child {node {$b$}
            child {node {$\{h_3\}$}}};
        \node at (10, 0) {$M_x\colon$};
        \node at (11.5, 0) {1}
          child {node {$a$}
            child {node {$\{[h_2]\}$}}};
        \node at (15, 0) {$M_y\colon$};
        \node at (16.5, 0) {1}
          child {node {$b$}
            child {node {$\{[h_2]\}$}}};
      \end{tikzpicture}
    \end{minipage}
  \end{subcaptiongroup}
  \caption{Rule states encountered during Examples~1 and~2}
\end{figure}
